%% arara: clean: { files: [cv_egon_geerardyn.aux, cv_egon_geerardyn.bbl, phdthesis.acn, phdthesis.acr, cv_egon_geerardyn.out, cv_egon_geerardyn.blg, cv_egon_geerardyn.log, cv_egon_geerardyn.run.xml, cv_egon_geerardyn.bcf] }
% arara: vc
% arara: xelatex: { shell : yes, synctex : yes, options : "-8bit" }
% arara: xelatex: { shell : yes, synctex : yes, options : "-8bit" }

\documentclass[]{cv-egeerardyn}

\usepackage{xspace}

\firstName{Egon}
\lastName{Geerardyn}
\tagLine{Electronics Engineer with a passion for IT}
\maritalStatus{not married}

\address{Zomerstraat 26 GV 00\\1050 Brussels (Belgium)}
\email{egon.geerardyn@gmail.com}
% \website{egeerardyn.github.io}
\phone{+32 472 65 61 08}

\birthDate{15 April 1988}
\nationality{Belgian}
\birthPlace{Jette (BE)}

\profileGithub{egeerardyn}
\profileLinkedIn{egongeerardyn}
\profileResearchGate{Egon\_Geerardyn}
\profileStackOverflow{Egon}{514071}

\begin{document}
\maketitle

\newcommand{\VUB}{Vrije Universiteit Brussel}
\newcommand{\TUe}{Technische Universiteit Eindhoven}
\newcommand{\Stanford}{Stanford}
\newcommand{\EPFL}{EPFL}
\newcommand{\CST}{Control System Technology}
\newcommand{\TikZ}{\mbox{Ti\emph{k}Z}\xspace}
\newcommand{\PK}{Polytechnische Kring}
\newcommand{\ELEC}{ELEC}

\begin{education}
  \addEducation[prospect\\ June 2016]{2011 -- 2016}{PhD Electrical Engineering}{\VUB}
  {In my research on user-friendly identification of linear systems, I gained expertise in system identification and measurements. During my two-month stay at the \CST{} group at the \TUe, I improved my proficiency in robust control and applied my research in the field.}

  \addEducation{2006 -- 2011}{BSc \& MSc Electrical Engineering and IT (ir.)}{\VUB}
  {In my thesis ``A Simulation Method for Pinpointing the Dominant Nonlinear Contributors in CMOS Circuits'' I wrote a tool in \keyword{ANTLR}, \keyword{Java} and \keyword{MATLAB} that performs a labor-intensive Volterra analysis on electrical circuits. For this work I received the IMEC award for best master thesis at the VUB.}

  \addText{2011 -- now}{I continually strive to perfect my abilities by taking courses such as 
  \keyword{LabView Core 2}
  and 
  \keyword{LabView FPGA}, 
  hence I became a \keyword{Certified LabView Associate Developer}
  in 2014. 
  I have successfully completed online courses such as 
  {Convex Optimization}, 
  Functional Programming with Scala, 
  Machine Learning and 
  Introduction to Databases that were taught by experts from 
  \Stanford{} and 
  \EPFL{}.}

\end{education}

\begin{experience}
  \addJob{2012 -- now}{Major contributor and maintainer (since 2015)}{github:matlab2tikz}{
  I maintain the open-source \code{matlab2tikz} program that converts \keyword{MATLAB}  figures to \keyword{\TikZ} (\keyword{\LaTeX}) code.
  This program is one of the ten most-downloaded programs for MATLAB.
  }

  \addJob[summers]{2009 -- 2011}{Engineering summer jobs}{\ELEC (\VUB)}{
For the system identification and electrical measurements courses, I made course notes, lab instructions and measurement set-ups using \keyword{LabView} and \keyword{NI Elvis II}.}

  \addJob{2007 -- 2009}{Web master and server admin}{\PK}{
  For my engineering fraternity, I updated the website to \keyword{PHP} / \keyword{Joomla} and helped to maintain the \keyword{Gentoo Linux} web server running \keyword{Apache}.
  }
\end{experience}

\begin{languages}
  \addLanguage{Dutch}{Native}{}
  \addLanguage{English}{Advanced}{Daily use in an academic setting.}
  \addLanguage{French}{Intermediate}{I have been living in Ixelles (Brussels) since 2013.}
\end{languages}
\section{competences}

For my everyday work, I rely on \keyword{Mac OS X}, \keyword{MATLAB}, \keyword{SimuLink}, \keyword{LabView}, \keyword{Sage}, \keyword{LaTeX} and \keyword{git}. 
In previous projects, I have used \keyword{Python}, \keyword{ANTLR}, \keyword{Scala}, \keyword{Java}, \keyword{Delphi}, \keyword{assembly} and \keyword{VHDL} amongst others. 
As a teaching assistant, I taught \keyword{C} for \keyword{microcontroller} programming for electronics and control labs.


\end{document}
